### 2015-07-05 narrative/qos.tex
get my own bib in.
started to work on qos.

What else do we need to talk about?

@@

\paragraph{Background:} One of the key differentiating features this project offers is driving storage
decisions through quality of service (QoS) \emph{reservations} rather than continuing the current model of allowing
all application to compete, without restriction, for part or all of the storage
resources. This traditional approach leads to intereference
effects~\cite{lofstead:2010:adaptive} that can greatly impact IO performance
predictability. Further, with the introduction of additional tiers in the
storage stack, the performance variability will increase with greater
competiion for limited high performance resources. Unfettered, this competition
will yield lower performance for all users than if applications
attempt to reserve performance, thereby enabling the storage system
to reason over its performance in terms of reservations and actual
performance, accepting reservations that are within resource
availability, rejecting those that would lead to overload.

It is important to note that we use performance reservations to
reduce interference and to avoid overload conditions. If the system
uses reservations intelligently, its performance is predictable and
efficient because resources are not wasted on interference. However,
in cases where an appication arrives that needs to run more urgently
than any of the other already running applications, administrators
can suspend less urgent applications which will save their state
and relinquish their performance reservations. Upon restart, these
applications make new performance reservations.

>>>>

@@

\paragraph{Background:} One of the key differentiating features this project offers is driving storage
decisions through quality of service (QoS) \emph{reservations} rather than continuing the current model
of allowing applications to compete, without restriction, for part or all of the storage
resources. This traditional approach leads to intereference
effects~\cite{lofstead:2010:adaptive,liu_hotstorage} that can greatly impact IO performance
predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for the next DOE systems. 
Unfettered, this competition will yield lower performance for all users than if applications
attempt to reserve performance, thereby enabling the storage system
to reason over its performance in terms of reservations and actual
performance, accepting reservations that are within resource
availability, rejecting those that would lead to overload.

{\bf {\color{red}Will connect to text on policies. Gary}}

It is important to note that we use performance reservations to
reduce interference and to avoid overload conditions. If the system
uses reservations intelligently, its performance is predictable and
efficient because resources are not wasted on interference. However,
in cases where an appication arrives that needs to run more urgently
than any of the other already running applications, administrators
can rapidly respond to it by reducing the amount of resources taken 
by less urgent applications, allowing the urgent application to finish,
and reverting back to the previous committed resource level.
